---
title: "Demo on how the empirical Gaussian prior was implemented"
output:
  html_document:
    df_print: paged
---

Assume that the log-$\alpha$-modified posterior follows a normal distribution
$p(\log(\alpha),\beta|D) \sim \mathcal{N}(\mu,\Sigma)$.
Assume an unknown true $\mu$, $\Sigma$ as:

```{r}
log_theta <- c("log_alpha", "beta")
theta     <- c("alpha", "beta")
resolution <- c(alpha=20, beta=20)
n_sample <- 200

(mu <- c(log_alpha=1, beta=2))
(sigma <- matrix(c(1, -.8, -.8, 1), 2, dimnames=list(log_theta, log_theta)))
```

Sample from it to get a sense of its shape:

```{r, echo=FALSE}
suppressMessages(library(mixtools))
```

```{r}
x <- rmvnorm(n_sample, mu, sigma)
colnames(x) <- log_theta
plot(x, xlim=mu["log_alpha"] + c(-4, 4), ylim=mu["beta"] + c(-4, 4), asp=TRUE)
```

Create a parameter grid similar to that created by ADEBA.
Note that the grid is _linear_ over $\alpha$ since a logarithmically spaced grid
would mess up the Bayesian model averaging.

```{r}
parts <- lapply(mu["beta"] + seq(-3.5, 3.5, length.out = resolution["beta"]), function(beta){
  m <- mu["log_alpha"] - (beta - mu["beta"]) + .3*rnorm(1)
  log_r <- 4 + .3*rnorm(1)
  
  data.frame(
    #alpha.range = unname( exp(m+log_r/2) - exp(m-log_r/2) ),
    alpha       = seq(exp(m-log_r/2), exp(m+log_r/2), length.out = resolution["alpha"]),
    beta        = beta
  )
})
param <- do.call(rbind, parts)
#param
```

Overlay grid on the data to see that it looks sensible:

```{r}
par(mfrow=1:2, mar=c(3, 3, .4, .4), mgp=c(1.8, .5, 0))

plot(x, xlim=mu["log_alpha"] + c(-4, 4), ylim=mu["beta"] + c(-4, 4))
points(log(param$alpha), param$beta, col="red", pch=20, cex=.5)

plot(exp(x[,1]), x[,2],
     xlim=exp(mu["log_alpha"] + c(-4, 4)),
     ylim=mu["beta"] + c(-4, 4),
     xlab="alpha", ylab="beta")
points(param[,theta], col="red", pch=20, cex=.5)
```

Estimate $\hat{\mu}$, $\hat{\Sigma}$ from the data.

```{r, echo=FALSE}
suppressMessages(library(dplyr))
```

```{r}
px <- cbind(
  log_alpha = log(param$alpha),
  beta      = param$beta
)
param$likelihood <- dmvnorm(px, mu = mu, sigma = sigma)

weights <- with(
  merge(
    param,
    aggregate(alpha ~ beta, param, function(x) sum(1/x)),
    by="beta"
  ),
  likelihood / (alpha.x * alpha.y)
)

cov.wt(px, wt=weights)[c("cov", "center")]
```
